---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lasers

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of lasers is to make the FAA laser incidents data available.

## Development Version

You can install the development version with the code below:

```{r, install, eval=F}
# install.packages("devtools")
devtools::install_github("RobWiederstein/lasers)
```

## Usage

```{r, usage}
library(lasers)
head(lasers) |> tibble::tibble()

```

## Acknowledgements

Many thanks to the following persons, entities and agencies for making the project possible:

- The U.S. Federal Aviation Administration

## Code of Conduct
  
Please note that the lasers project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

